Detect_MHWs

### 2019-04-08 Exploring/Detect_MHWs.Rmd
housekeeping

---
title: "Long_time_series"
author: "Amieroh Abrahams"
date: "04 February 2019"
output: html_document
---

# Script Info (Time series)

The first few lines of this script only looks at a time series of 10 years or greater. However, from line 360 a longer time series is used. This time series has a length of greater than 30 years and so only a few sites are used. With a longer time series I am able to detect for extreme events such as Marine Cold Spells (MCSs).

** This script is very repetitive. Wavelet.Rmd creates a function to do this **

@@

## Selecting the sites and creating new *in situ* datasets
Now we select only the sites occuring along the west coast. Thereafter, I include all the sites which had a time series of 10 years or greater.

```{r}

# # Upwelling Cell 1:
# site_list_sub <- site_list %>%
#   filter(coast == "wc") %>%
#   filter(length > 3650)
# 
# # upwelling_sites <- site_list_sub[-6,] # Here we had two rows of data for Paternoster; i removed the DEA row: All data here are now collected by SAWS
# upwelling_sites <- upwelling_sites[-10:-14,]
# 
# # # # Here I find a time series with the data with a relativley long time series
# UC_1 <- upwelling_sites[c(-2, -3, -5, -6, -8),]
# save(UC_1, file = "Data/UC_1.RData")
# SACTN_daily_temps <- SACTN_daily_v4.2 %>%
#   left_join(site_list[,c(4,13)], by = "index") %>%
#   filter(index %in% upwelling_sites$index)
# save(SACTN_daily_temps, file = "Data/SACTN_daily_temps.RData")
# # 
# SACTN_US1 <- SACTN_daily_temps %>%
#   separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>%
#   dplyr::rename(insitu_temp = temp)
# save(SACTN_US1, file = "Data/SACTN_US1.RData")

# Upwelling Cell 2:
# site_list_sub_UC <- site_list %>%
#   filter(coast == "wc") %>%
#   filter(length > 3650)
# 
# upwelling_sites_UC <- site_list_sub_UC[-1:-8,]
# UC_2 <- upwelling_sites_UC[c(-2,-5),] # New sites falling within the upwelling cell before yzerfontein
# save(UC_2, file = "Data/UC_2.RData")
# 
# 
# SACTN_daily_temps_UC <- SACTN_daily_v4.2 %>%
#   left_join(site_list[,c(4,13)], by = "index") %>%
#   filter(index %in% upwelling_sites_UC$index)
# save(SACTN_daily_temps, file = "Data/SACTN_daily_temps.RData")
# 
# SACTN_US2 <- SACTN_daily_temps_UC %>%
#   separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>%
#   dplyr::rename(insitu_temp = temp)
# 
# save(SACTN_US2, file = "Data/SACTN_US2.RData")

####################################################################################

# combined_US <- rbind(UC_1,UC_2)
#save(combined_US, file = "Data/combined_US.RData")
SACTN_temps_US <- SACTN_daily_v4.2 %>%
  left_join(site_list[,c(4,13)], by = "index") %>%
  filter(index %in% combined_US$index)

SACTN_temps_US <- SACTN_temps_US %>%
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>%
  dplyr::rename(insitu_temp = temp)

# save(SACTN_temps_US, file = "Data/SACTN_temps_US.RData")
```

I now create two datasets, `SACTN_split_US1` and `SACTN_split_US2`. These two datasets represents different groups of sites within the upwelling center based on the location of each of the sites. `SACTN_split_US1`: Port Nolloth, Lamberts Bay, Saldanna and Yzerfontein. `SACTN_split_US2`: Dassen Island, Sea Point, Hout Bay and Kommetjie. Here I also add monthly, yearly and seasonal column. This allows us to compare temperature variation on a seasonal basis. Research studies done suggests that the intensity and duration of upwelling varies on a seasonal basis.

```{r}
SACTN_monthly <- function(df) {
  SACTN_split_monthly <- df %>%
  mutate(month = month(date, abbr = T, label = T),
         year = year(date)) %>%
  group_by(index, month, year) %>%
    mutate(season = ifelse(month %in% c("Jan", "Feb", "Mar"), "Summer",       
                           ifelse(month %in% c("Apr", "May", "Jun"), "Autumn",
                                ifelse(month %in% c("Jul", "Aug", "Sep"), "Winter",
                                       ifelse(month %in% c("Oct", "Nov", "Dec"), "Spring","Error")))))
  return(SACTN_split_monthly)
}

# SACTN_split_US1 <- SACTN_monthly(df = SACTN_US1)
# SACTN_split_US2 <- SACTN_monthly(df = SACTN_US2)
# save(SACTN_split_US1, file = "SACTN_split_US1.RData")
# save(SACTN_split_US2, file = "SACTN_split_US2.RData")
```

Find where different sites have overlapping time series within this `SACTN_temps_US` dataset. Finding a long time series.

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/combined_US.RData")
load("~/Documents/Masters_2019/MastersProject/Data/SACTN_temps_US.RData")
# Find a period where each of the sites within that overlap.

overlap_ts <- SACTN_temps_US %>% 
  filter(year(date) %in% seq(1992, 2016)) %>% # The length of the time may vary depending on the question
  drop_na() # Removing NA values within the dataset
save(overlap_ts, file = "Data/overlap_ts.RData")

temp_plot <- function(df){
  plot <- ggplot(data = df, aes(x = date, y = insitu_temp, colour = site)) +
    geom_line(aes(group = site)) +
    labs(x = "", y = "Temperature (°C)") +
    theme(axis.text.x = element_text(angle = 45)) +
    theme(legend.position = "top")
}

SACTN_temps_US_plot <- temp_plot(df = overlap_ts)
```

In this thesis, different remotely-sensed SST datasets are used. Hence, these datasets represent different resolutions at which data was obtained. We will make use of five remotely-sensed SST datasets, these include; the  MUR, AVHRR OISST, K10 and G1SST data. **MODIS SST data need to be downloaded and used too**

## MUR dataset
```{r}
MUR_Lamberts_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR_nearest5pixels/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Yzerfontein <- read_csv("Data/MUR_nearest5pixels/MUR_Yzerfontein_SST_timeseries_5nearest.csv")
MUR_Dassen_Island <- read_csv("Data/MUR_nearest5pixels/MUR_Dassen Island_SST_timeseries_5nearest.csv")
MUR_Hout_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Hout Bay_SST_timeseries_5nearest.csv")
MUR_Kommetjie <- read_csv("Data/MUR_nearest5pixels/MUR_Kommetjie_SST_timeseries_5nearest.csv")
MUR_Sea_Point <- read_csv("Data/MUR_nearest5pixels/MUR_Sea Point_SST_timeseries_5nearest.csv")
MUR_Oudekraal <- read_csv("Data/MUR_nearest5pixels/MUR_Oudekraal_SST_timeseries_5nearest.csv")

MUR_SST <- rbind(MUR_Lamberts_Bay,MUR_Yzerfontein, MUR_Port_Nolloth,MUR_Saldanha_Bay, MUR_Dassen_Island, MUR_Hout_Bay, MUR_Kommetjie, MUR_Sea_Point, MUR_Oudekraal) %>%
  dplyr::rename(site = station)

MUR_SST$date <- (ymd(MUR_SST$date))
# save(MUR_SST, file = "Data/MUR_SST.RData")

load("~/Documents/Masters_2019/MastersProject/Data/MUR_SST.RData")
MUR_SST <- MUR_SST %>% 
  drop_na()
```

This function matches the remotely-sensed SST to the *in-situ* collected SST

```{r}
MUR_SST <- MUR_SST %>% 
  dplyr::rename(temp = nearest1) # nearest1- 1 pixel as applied to the OISST data

match_func <- function(df){
  match <- overlap_ts  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}
insitu_MUR <- match_func(df = MUR_SST) %>%
  drop_na()
# save(insitu_MUR, file = "Data/insitu_MUR.RData")

match_plot <- function(df){
  plot1 <- df %>% 
ggplot(aes(x = date, y = temp)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 2) +
  theme_bw()
  return(plot1)
}
MUR_plot <- match_plot(df = insitu_MUR)

temp_plot <- function(df){
  temp_plot <- df %>% 
  ggplot(aes(x = date, y = temp, colour = site)) +
    geom_line(aes(group = site)) +
    labs(x = "", y = "Temperature (°C)") +
    theme(axis.text.x = element_text(angle = 45)) +
    theme(legend.position = "top")
}
MUR_plot <- temp_plot(df = insitu_MUR)
```

## OISST dataset
```{r}
# AVHRR <- read_csv("data/csvavhrr-only-v2-19810901-20180630.csv")

# OISSTDir <- "~/Documents/Masters_2019/Data_SST"
# OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
#             col.names = c("lon", "lat", "temp", "date"))

OISST <- as.tibble(fread("Data/csvavhrr-only-v2-19810901-20180630.csv"))
# # Quick visualisation of the data
# # To explore the data I visualise the min temperatures along the South african coastline.
# 
# OISST %>%
#   filter(date == min(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
# ggsave(plot = OISST, filename = "Figures/OISST")
```

## Here I find the nearest SST pixels

Now we apply the FNN (Fast Nearest Neighbor) package to determine the nearesr SST pixel to the insitu collected sites.

```{r}
# unique_pixel <- OISST %>%
#   select(lon, lat) %>%
#   unique()
# 
# # Select nearest 1 pixels (k = 1)
# # here we use knnx to find the closes 1 pixels to the insitu sites
# match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
#                           query = as.matrix(combined_US[,5:6]), k = 1)
# 
# # Select SST pixels nearest to insitu sites
# pixel_match <- unique_pixel[match_index,] %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   mutate(site = combined_US$site)
# 
# ## Subsetting the OISST data to match the upwelling sites within the in situ collected temperature data
# OISST_match <- OISST %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   filter(combi %in% pixel_match$combi)
# 
# ## Visualisation
# ggplot(data = OISST_match, aes(x = date, y = temp_OISST)) +
#   geom_line() +
#   facet_wrap(~combi)
# ggsave(plot = OISST_match, filename = "Figures/combined_OISST_match")
# 
# OISST_match %>%
#   filter(date == max(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
```

```{r}
# OISST_sites <- OISST_match %>%
#   left_join(pixel_match, by = c("combi", "lon", "lat")) %>% 
#   dplyr::rename(temp_OISST =temp)
# 
# # Check that the pixel that is shared is duplicated
# # unique(combined_OISST_sites$site)
# # Visualise time series
# ggplot(data = OISST_sites, aes(x = date, y = temp)) +
#   geom_line() +
#   facet_wrap(~site)

# save(OISST_sites, file = "Data/OISST_sites.RData")
load("~/Documents/Masters_2019/MastersProject/Data/OISST_sites.RData")
OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
```

## Matching the Insitu data with the OISST SST data
```{r}
insitu_OISST <- match_func(df = OISST_sites)
# save(insitu_OISST, file = "Data/insitu_OISST.RData")
OISST_plot <- match_plot(df = insitu_OISST)
OISST_temp_plot <- temp_plot(df = insitu_OISST)
```

## G1SST dataset
```{r}
Lamberts_Bay <- read_csv("Data/G1SST_sub/Lamberts Bay_SST_timeseries_5nearest.csv")
Port_Nolloth <- read_csv("Data/G1SST_sub/Port Nolloth_SST_timeseries_5nearest.csv")
Saldanha_Bay <- read_csv("Data/G1SST_sub/Saldanha Bay_SST_timeseries_5nearest.csv")
Yzerfontein <- read_csv("Data/G1SST_sub/Yzerfontein_SST_timeseries_5nearest.csv")
Dassen_Island <- read_csv("Data/G1SST_sub/Dassen Island_SST_timeseries_5nearest.csv")
Hout_Bay_SST <- read_csv("Data/G1SST_sub/Hout Bay_SST_timeseries_5nearest.csv")
Kommetjie_SST <- read_csv("Data/G1SST_sub/Kommetjie_SST_timeseries_5nearest.csv")
Oudekraal_SST <- read_csv("Data/G1SST_sub/Oudekraal_SST_timeseries_5nearest.csv")
Sea_Point_SST<- read_csv("Data/G1SST_sub/Sea Point_SST_timeseries_5nearest.csv")

G1SSTsub_SST <- rbind(Lamberts_Bay,Port_Nolloth, Saldanha_Bay, Yzerfontein, Dassen_Island, Hout_Bay_SST, Kommetjie_SST, Oudekraal_SST, Sea_Point_SST) %>%
  dplyr::rename(site = station)

G1SSTsub_SST$date <- (ymd(G1SSTsub_SST$date))
save(G1SSTsub_SST, file = "Data/G1SSTsub_SST.RData")

# load("Data/G1SSTsub_SST.RData")

G1SSTsub_SST <- G1SSTsub_SST %>% 
  drop_na() %>% 
  dplyr::rename(temp = nearest1)

insitu_G1SST <- match_func(df = G1SSTsub_SST) 
# save(insitu_G1SST, file = "Data/insitu_G1SST.RData")
G1SST_plot <- match_plot(df = insitu_G1SST )
G1SST_temp_plot <- temp_plot(df = insitu_G1SST)
```

# K10
```{r}
Lamberts_Bay <- read_csv("Data/K10/K10_Lamberts Bay_SST_timeseries_5nearest.csv")
Port_Nolloth <- read_csv("Data/K10/K10_Port Nolloth_SST_timeseries_5nearest.csv")
Saldanha_Bay <- read_csv("Data/K10/K10_Saldanha Bay_SST_timeseries_5nearest.csv")
Yzerfontein <- read_csv("Data/K10/K10_Yzerfontein_SST_timeseries_5nearest.csv")
Dassen_Island <- read_csv("Data/K10/K10_Dassen Island_SST_timeseries_5nearest.csv")
Hout_Bay <- read_csv("Data/K10/K10_Hout Bay_SST_timeseries_5nearest.csv")
Kommetjie <- read_csv("Data/K10/K10_Kommetjie_SST_timeseries_5nearest.csv")
Oudekraal <- read_csv("Data/K10/K10_Oudekraal_SST_timeseries_5nearest.csv")
Sea_Point <- read_csv("Data/K10/K10_Sea Point_SST_timeseries_5nearest.csv")

K10_SST <- rbind(Lamberts_Bay, Yzerfontein, Port_Nolloth, Saldanha_Bay, Dassen_Island, Hout_Bay, Kommetjie, Oudekraal, Sea_Point) %>%
  dplyr::rename(site = station)
K10_SST$date <- (ymd(K10_SST$date))
# save(K10_SST, file = "Data/K10_SST.RData")

load("~/Documents/Masters_2019/MastersProject/Data/K10_SST.RData")
K10_SST <- K10_SST %>% 
  drop_na()
K10_SST <- K10_SST %>% 
  dplyr::rename(temp = nearest1)

insitu_K10 <- match_func(df = K10_SST) 
# save(insitu_K10, file = "Data/insitu_K10.RData")
K10_plot <- match_plot(df = insitu_K10)
k10_temp_plot <- temp_plot(df = insitu_K10)
```

@@

# Anatomy of marine cold spells within the upwelling center
Make use of the make_whole_fast function within the heatwaveR package. This function constructs a continuous, uninterrupted time series of temperatures (faster).

@@

ts <- ts2clm(MUR_SST_PN, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_PN")

@@

ts <- ts2clm(MUR_SST_LB, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_LB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_LB")

@@

ts <- ts2clm(MUR_SST_YZ, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_YZ")

@@

ts <- ts2clm(MUR_SST_SB, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_SB")

@@

ts <- ts2clm(MUR_SST_SP, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_SP")

@@

ts <- ts2clm(MUR_SST_O, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_O <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_O")

@@

ts <- ts2clm(MUR_SST_Kom, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_Kom")

combined_MUR <- ggarrange(MCS_MUR_PN, MCS_MUR_LB, MCS_MUR_O, MCS_MUR_SP, MCS_MUR_KoM, MCS_MUR_SB, MCS_MUR_YZ, ncol = 2, nrow = 4)
```

@@

ts <- ts2clm(G1SSTsub_SST_PN, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_PN")

@@

ts <- ts2clm(G1SSTsub_SST_LB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_LB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_LB")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SB")

@@

ts <- ts2clm(G1SSTsub_SST_YZ, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_YZ")

@@

ts <- ts2clm(G1SSTsub_SST_SP, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SP")

@@

ts <- ts2clm(G1SSTsub_SST_O, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_O <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_O")

@@

ts <- ts2clm(G1SSTsub_SST_Kom, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_Kom")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SB")

combined_G1SST <- ggarrange(MCS_g1sst_PN, MCS_g1sst_LB, MCS_g1sst_O, MCS_g1sst_SP, MCS_g1sst_Kom, MCS_g1sst_YZ, MCS_g1sst_SB, ncol = 2, nrow = 4)
```

@@

ts <- ts2clm(OISST_PN, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_PN <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_PN")

@@

ts <- ts2clm(OISST_LB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_LB <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_LB")

@@

ts <- ts2clm(OISST_SB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_SB")

@@

ts <- ts2clm(OISST_YZ, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_YZ")

@@

ts <- ts2clm(OISST_SP, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_SP")

@@

ts <- ts2clm(OISST_Kom, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_Kom")

@@

ts <- ts2clm(OISST_O, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_O <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_O")

combined_OISST <- ggarrange(MCS_OISST_PN, MCS_OISST_LB, MCS_OISST_SB, MCS_OISST_YZ, MCS_OISST_O, MCS_OISST_Kom,MCS_OISST_SP, ncol = 2, nrow = 4)
```

# K10
Time series is less than 10 years and so the detection of MCS is not effective. 
heatwaveR package may be applied to datasets that have a climatological period of >10years

```{r}

>>>>

---
title: "Detect_MHWs"
author: "Amieroh Abrahams"
date: "02 April 2019"
output: html_document
---

@@

@@

# Anatomy of marine heatwaves within the upwelling center
Make use of the make_whole_fast function within the heatwaveR package. This function constructs a continuous, uninterrupted time series of temperatures (faster).

@@

ts <- ts2clm(MUR_SST_PN, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_MUR_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_PN")

@@

ts <- ts2clm(MUR_SST_LB, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_MUR_LB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_LB")

@@

ts <- ts2clm(MUR_SST_YZ, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_MUR_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_YZ")

@@

ts <- ts2clm(MUR_SST_SB, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_MUR_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_SB")

@@

ts <- ts2clm(MUR_SST_SP, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_MUR_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_SP")

@@

ts <- ts2clm(MUR_SST_O, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_MUR_O <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_O")

@@

ts <- ts2clm(MUR_SST_Kom, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_MUR_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_Kom")

combined_MUR <- ggarrange(MHW_MUR_PN, MHW_MUR_LB, MHW_MUR_O, MHW_MUR_SP,MHW_MUR_Kom, MHW_MUR_SB, MHW_MUR_YZ, ncol = 2, nrow = 4)
```

@@

ts <- ts2clm(G1SSTsub_SST_PN, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_PN")

@@

ts <- ts2clm(G1SSTsub_SST_LB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_LB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_LB")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SB")

@@

ts <- ts2clm(G1SSTsub_SST_YZ, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_YZ")

@@

ts <- ts2clm(G1SSTsub_SST_SP, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SP")

@@

ts <- ts2clm(G1SSTsub_SST_O, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_O <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_O")

@@

ts <- ts2clm(G1SSTsub_SST_Kom, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_Kom")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 90)
res <- detect_event(ts)
MCS <- res$climatology
MHW_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SB")

combined_G1SST <- ggarrange(MHW_g1sst_PN, MHW_g1sst_LB, MHW_g1sst_O, MHW_g1sst_SP, MHW_g1sst_Kom, MHW_g1sst_YZ, MHW_g1sst_SB, ncol = 2, nrow = 4)
```

@@

ts <- ts2clm(OISST_PN, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 90)
res <- detect_event(ts)
MHW_OISST_PN <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_PN")

@@

ts <- ts2clm(OISST_LB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 90)
res <- detect_event(ts)
MHW_OISST_LB <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_LB")

@@

ts <- ts2clm(OISST_SB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 90)
res <- detect_event(ts)
MHW_OISST_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_SB")

@@

ts <- ts2clm(OISST_YZ, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 90)
res <- detect_event(ts)
MHW_OISST_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_YZ")

@@

ts <- ts2clm(OISST_SP, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 90)
res <- detect_event(ts)
MHW_OISST_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_SP")

@@

ts <- ts2clm(OISST_Kom, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 90)
res <- detect_event(ts)
MHW_OISST_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_Kom")

@@

ts <- ts2clm(OISST_O, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 90)
res <- detect_event(ts)
MHW_OISST_O <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_O")

combined_OISST <- ggarrange(MHW_OISST_PN, MHW_OISST_LB, MHW_OISST_SB, MHW_OISST_YZ, MHW_OISST_O, MHW_OISST_Kom,MHW_OISST_SP, ncol = 2, nrow = 4)
```
